Guided Proofreading of Automatic Segmentations for Connectomics

### 2017-11-14 paper/introduction.tex
James going through the edits.

This paper makes the following contributions.
%
First, we present a CNN-based boundary classifier for split errors, plus a merge
error classifier that inverts the split error classifier. This is used to
propose merge error corrections, removing the need to manually draw the missing
edge. These classifiers perform well without much training data, which is
expensive to collect for connectomics data.
%
Second, we developed a guided proofreading approach to correcting segmentation
volumes, and an assessment scenario comparing forced-choice interaction with
automatic and oracle proofreading.
%
Third, we present the results of a quantitative user study assessing
guided proofreading. Our method is able to reduce segmentation
error faster than state-of-the-art semi-automatic tools for both novice and
expert users.
%
\CHANGED{Finally, we present the first standardized benchmark for proofreading in connectomics as an open research platform.}

Guided proofreading is applicable to all existing automatic segmentation methods that
produce a label map. As such, we believe that our approach is a promising
direction to proofread segmentations more efficiently and better tackle large
volumes of connectomics imagery.

>>>>

This paper makes the following contributions.
%
First, we present a CNN-based boundary classifier for split errors, plus a merge
error classifier that inverts the split error classifier. This proposes merge error corrections, 
which removes the need to manually draw the missing
edge. \CHANGED{These classifiers automatically reduce error with little training data,} which is
expensive to collect for connectomics data.
%
Second, we develop a \CHANGED{human-}guided proofreading approach to correcting segmentation
volumes, and compare forced-choice interaction with
automatic and oracle proofreading.
%
Third, we present results of a quantitative user study assessing
guided proofreading. Our method is able to reduce segmentation
error faster than state-of-the-art semi-automatic tools for both novice and
expert users.
%
\CHANGED{Fourth, we present the first connectomics proofreading benchmark, with image, label, and human interaction data, and evaluation code.}

Guided proofreading is applicable to all existing automatic segmentation methods that produce a label map.
\CHANGED{While we train models based on traditional CNN architectures, we propose an error correction approach with human interaction that works with many classifiers.}
As such, we believe that our approach is a promising direction to proofread segmentations more efficiently and better tackle large volumes of connectomics imagery.

### 2017-11-14 paper/related_work.tex
James going through the edits.

Karimov \etal~\cite{karimov_guided_volume_editing} propose guided volume editing, which measures the difference in histogram distributions in image data to find potential split and merge errors in the corresponding segmentation. This lets expert users correct labeled computer-tomography datasets, using several interactions per correction. To correct merge errors, the authors create a large number of superpixels within a single segment and then successively group them based on dissimilarities. We were inspired by this approach, but instead we generate single watershed boundaries to handle the intracellular variance in high-resolution EM images (Sec.~\ref{sec:methods}).

>>>>

Karimov \etal~\cite{karimov_guided_volume_editing} propose guided volume editing, which measures the difference in histogram distributions in image data to find potential split and merge errors in the corresponding segmentation. This lets expert users correct labeled computer-tomography datasets, using several interactions per correction. To correct merge errors, the authors create a large number of superpixels within a single segment and then successively group them based on dissimilarities. We were inspired by this approach, but instead we generate single watershed boundaries to handle the intracellular variance in high-resolution EM images (Sec.~\ref{sec:methods}). \CHANGED{Recently, Zung \etal~\cite{error_detection_framework} report the successful application of 3D multiscale convolutional neural networks for error detection and correction as a post-processing step after segmentation. Their framework is purely automatic, and can be used as input to our proposed method.}
